Aneuploidy can be an evolutionary detour \\ on the path to adaptation

### 2022-10-30 ms/ms.tex
OD revised sequencing paragraph

%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{DNA sequencing.}
Whole-genome sequencing of the ancestral diploid strain (\euwt) was performed on a sample from a single colony of the ancestor.
Whole-genome sequencing of the four evolving populations ($H2$ after 450 and 2,350 generations, and $H4$ after 450 and 1,700 generations) was performed on a sample from these populations (rather than from single colonies).
The liquid sample from each evolving population was taken from each culture as it grows under the same conditions as the lab evolution experiments (YPD at \SI{39}{\celsius}).
DNA was purified from the collected cells for each population and downstream deep sequencing was performed according to the Illumina protocol for amplicon sequencing.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{DNA sequencing.}
Whole-genome sequencing of the ancestral diploid strain (\euwt) was performed
on a single colony of the ancestor. Whole-genome sequencing of the four evolving populations ($H2$ after 450 and 2,350 generations, and $H4$ after 450 and 1,700 generations) was performed on a sample from these populations (rather than from single colonies) in order to maintain the population diversity. Cells were grown in 5ml of YPD medium, either at \SI{30}{\celsius} (ancestral diploid) or \SI{39}{\celsius} (evolved populations) in shaking conditions (200rpm) until reaching stationary phase. Following growth, 3ml of each culture were centrifuge (14,000rpm) and cell pellets were used for DNA extraction. 
Genomic DNA was extracted using “MasterPure Yeast DNA Purification Kit” (Lucigen) according to the manufacture instructions. Following extraction, DNA concentrations were determined by Qubit assay (Thermo Fisher) and ~1µg DNA was used for library preparation using Illumina sample preparation kit (Illumina). Samples were sequenced using a 100 bp pair end read output run using Illumina HiSeq2500.
